manuscript - APP

### 2018-12-05 R/manuscript_app.Rmd

```{r load data - exp 1a}
df_exp1a <- readRDS(file.path(data_pth,"exp1a","responses","responses_150330.rds")) %>% 
  filter(block != 0) %>% 
  filter(restk != "64") %>% # originally, we colledcted three levels of variaiblity, but the condition with kappa=64 showed similar results as kappa = 16
  as_data_frame() %>% 
  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like"))

@@

p1 <- traj_k64 %>% 
  filter(t > 10) %>%
  filter(object %in% c("o1","o2","o7","o3","o5")) %>% 
  ggplot(aes(xcoord, ycoord, group = object)) + 
  geom_path(size = 0.5) + 
  theme(aspect.ratio = 1) + 
  xlim(-15,15) +
  ylim(-15,15) +
  #scale_linetype_manual(values=c("solid", "solid")) + 
  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o3","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
  #geom_point(data = traj_k64 %>% filter(t==max(t),object %in% c("o1","o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
  guides(color = FALSE) +
  xlab("x [deg]") +
  ylab("y [deg]") +
  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64")) +
  theme(plot.title = element_text(hjust = 0.5))
p1
ggsave(here::here("..", "plots", "Figure2.png"), p1, width = 6, height = 6)

@@

```{r exp 1a - overall differences, warning=F, message = F}
df_exp1a %>% 
  filter(restk2 == "Brownian-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

@@

We run multiple within subject anova

```{r exp 1b - compute the assymetry, warning=F,eval = FALSE}
df3_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(p=compute.p(.))

df3_exp1b$p <- unlist(df3_exp1b$p) %>% round(3)
df4_exp1b <- df2_exp1b %>% group_by(type, restk) %>% do(ges=compute.des(.))
df4_exp1b$ges <- unlist(df4_exp1b$ges) %>% round(2)
df3_exp1b$ges <- df4_exp1b$ges

df5_exp1b <- df2_exp1b %>% group_by(type, restk, version) %>% summarize(accuracy = mean(accuracy)) %>% 
  group_by(type, restk) %>%
  summarize(acc_diff = accuracy[version == "fix distractors' k"] - accuracy[version == "fix target's k"])

m <- matrix(df3_exp1b$ges, nrow = 5)
rownames(m) <- levels(df_exp1b$type)
colnames(m) <- levels(df_exp1b$type)
m[upper.tri(m,diag = T)] <- NA

df3_exp1b$ges <- as.vector(m)

m <- matrix(df3_exp1b$p, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1b$p <- as.vector(m)

m <- matrix(df5_exp1b$acc_diff, nrow = 5)
m[upper.tri(m, diag = T)] <- NA
df3_exp1b$acc_diff <- as.vector(m)

df3_exp1b$target_lower_than_dist <- df3_exp1b$acc_diff < 0
df3_exp1b %>% filter(target_lower_than_dist)

df3_exp1b %>% filter(p < .05)
```

@@

@@

>>>>

```{r load data - exp 1a}
df_exp1a <- readRDS(file.path(data_pth,"exp1a","responses","responses_150330.rds")) %>% 
  filter(block != 0) %>% 
  filter(restk != "64") %>% # originally, we colledcted three levels of variaiblity, but the condition with kappa=64 showed similar results as kappa = 16
  as_data_frame() %>% 
  mutate(restk2 = recode(restk, `4` = "Brownian-like", `16` = "Ballistic-like")) %>% 
  mutate(type2 = as.factor(type))

@@

p1 <- traj_k64 %>% 
  filter(t > 10) %>%
  filter(object %in% c("o1","o2","o7","o3","o5")) %>% 
  ggplot(aes(xcoord, ycoord, group = object)) + 
  geom_path(size = 0.5) + 
  theme(aspect.ratio = 1) + 
  xlim(-15,15) +
  ylim(-15,15) +
  #scale_linetype_manual(values=c("solid", "solid")) + 
  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o3","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1,  show.legend=FALSE) +
  #geom_point(data = traj_k64 %>% filter(t==max(t),object %in% c("o1","o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
  guides(color = FALSE) +
  xlab("x [deg]") +
  ylab("y [deg]") +
  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64")) +
  theme(plot.title = element_text(hjust = 0.5))
p1
ggsave(here::here("..", "plots", "Figure2.png"), p1, width = 6, height = 6)
ggsave(here::here("..", "plots", "Figure2.eps"), p1, width = 6, height = 6)

@@

```{r exp 1a - overall differences, warning=F, message = F}
df_exp1a %>% 
  filter(restk2 == "Brownian-like") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type2, 
        detailed = T,) %>% 
  apa::anova_apa()

@@

@@

## Overall test

```{r exp1b overtall test}

df_exp1b %>% 
  filter(contrast_abs!=0) %>% 
  ezANOVA(dv = accuracy, within = .(contrast_abs, target_straight), wid = id,
          detailed = T) %>% 
  apa::anova_apa(sph_corr = "none", es = "ges")

@@

## Overall test

```{r exp2b overtall test}

df_exp2b %>% 
  filter(contrast_abs!=0) %>% 
  ezANOVA(dv = accuracy, within = .(contrast_abs, target_faster), wid = id,
          detailed = T) %>% 
  apa::anova_apa(sph_corr = "none", es = "ges")
